Insight Into Lumbar Back Pain \subtitle{What the Lumbar Spine Tells About Your Life}

### 2014-08-18 draft.tex
Size Result section finished

\paragraph{The Error Term. }
Normally the error rate for a classification is calculated with $error = \frac{n_{classifiedCorrectly}} {n}$ where $n$ is the number of subjects.
%%
The metric usually works well for normally distributed variables.
%%
It distorts the result for other distribution types.
%%
If for example a variable indicating a disease is negative for 90\% of the subject and the classifier simply assigns all subjects to \emph{not ill} the error metric would yield an error of 10\%, even though it is very bad.
%%
Our error term therefore incorporates the discriminative power of each manifestation and is denoted as follows:
%%
%Therefore the discriminative power of each dimension in the equation
%error = 1 - \frac{\[ \sum_{m=0}^M \] \frac{M_{classifiedCorrectly}}{M_all}}{number of dimensions}
\begin{equation}
error = 1 - \frac{\sum_{m=0}^M \frac{m_{classifiedCorrectly}}{m_{all}}}{number_{dimensions}}
\end{equation}
$M$ represents the set of manifestation of each variable.
%%
The error is scaled to denote perfect classification with 0 and 1 is equal to random selection.
% The error rate has to be judged depending on the number of classes of the target variable.
% %%
% An error rate of 50\% for a target variable with two manifestations makes the classifier equal to throwing a coin.
% %%
% The same error rate is acceptable a target variable with more than two manifestations.
% %%
% Picking a value for a variable of four manifestations with an error rate of 50\% is better than the random selection (error rate of 75\%).
% %%
% The following scales the error rate so that 0 denotes perfect classification and 1 is equal to random selection.
% %%
% \begin{equation}
% error_{normalized} = \frac{error}{100 - \frac{100}{class number}}
% \end{equation}
%%
It allows for comparability of error rates between variables with different manifestation count.

@@

\subsubsection{Size Groups}
%%
Many previously described results can be associated to be confounded with subject size.
%%
Differences in the gender analysis are mostly due to the average height difference between males and females.
%%
For example, large subjects are already characterized by their rather straight spine.
%
The question is, whether the inter-group spine-variability parameter is enough for predicting other parameter or not.
%%
Dividing subjects into height groups potentially highlights classifications not confounded by body-height.
%%

\com{Schmerzparameter mit drin, aber nur mit komplexen bäumen}

\com{- Kinderanzahl: 630 cases, 3,7\% Fehlerrrate, liegt aber daran, dass die meisten Probanden kein Kind haben. Die Einteilung ist aktuell auch unsinnig, das erste Quantil hat (-.0004,0.8] Kinder. Die Probanden werden nicht sauber erkannt.}

@@

\com{Allgmeine Analyse der Daten mit einbringen. Hierfuer statistisch Auswertung machen, welche Parameter am meisten verwendet wurden bei der Kategorisierung. Nur Parameter verwenden, die genauer sind als 0.5\%, der Entscheidungsbaum kleiner als 15 ist und das Feature mindestens 100 Probanden enthält }

>>>>

\paragraph{The Error Term. }
Normally the error rate for a classification is calculated with $error = \frac{n_{classifiedCorrectly}} {n}$ where $n$ is the number of subjects.
%%
The metric usually works well for variables with uniform distribution.
%%
It distorts the result for other distribution types.
%%
If for example a variable indicating a disease is negative for 90\% of the subject and the classifier simply assigns all subjects to \emph{not ill} the error metric would yield an error of 10\%, even though it is very bad.
%%
Our error term therefore incorporates the discriminative power of each manifestation and is denoted as follows:
%%
%Therefore the discriminative power of each dimension in the equation
%error = 1 - \frac{\[ \sum_{m=0}^M \] \frac{M_{classifiedCorrectly}}{M_all}}{number of dimensions}
\begin{equation}
error = 1 - \frac{\sum_{m=0}^M \frac{m_{classifiedCorrectly}}{m_{all}}}{number_{dimensions}}
\end{equation}
$M$ represents the set of manifestation of each variable.
%%
The error is scaled to denote perfect classification with 0 and 1 is equal to random selection.
% The error rate has to be judged depending on the number of classes of the target variable.
% %%
% An error rate of 50\% for a target variable with two manifestations makes the classifier equal to throwing a coin.
% %%
% The same error rate is acceptable a target variable with more than two manifestations.
% %%
% Picking a value for a variable of four manifestations with an error rate of 50\% is better than the random selection (error rate of 75\%).
% %%
% The following scales the error rate so that 0 denotes perfect classification and 1 is equal to random selection.
% %%
% \begin{equation}
% error_{normalized} = \frac{error}{100 - \frac{100}{class number}}
% \end{equation}
%%
It allows for comparability of error rates between variables with different manifestation count.

@@

\subsubsection{Size Groups}
%%
Many previously described results can be associated to be confounded with subject size.
%%
Differences in the gender analysis are mostly due to the average height difference between males and females.
%%
For example, large subjects are already characterized by their rather straight spine.
%
The question is, whether the inter-group spine-variability parameter is enough for predicting other parameter or not.
%%
Dividing subjects into height groups potentially highlights classifications not confounded by body-height.
%%
\paragraph{Large Decision Trees. }
Back-pain associated variables can be explained for various size-groups, but we could not extract universal rules.
%%
Radiating back pain could be described with error rate of $0,39$ using 23 rules for subjects between $171-177 cm$ body size using torsion and mean-curvature.
%%
For subjects sized $177-202 cm$ the accuracy drops to $0,47$ using 20  decision rules.
%%
There are several decision trees for laboratory values, such as alanine aminotransferase value in the blood can be described with a high precision of $0,4$ ($139-164 cm$) to $0,36$ ($164 - 171 cm$).
%%
Similar values can be observed for cholesterol or age.
%%
Due to the large decision trees, these results are not usable and impose overfitting to the data.
%%
\paragraph{Small Decision Trees. }
%%
The dummy variables show several variables described using only one decision rule with accuracy between $0,42$ to $0,47$.
%%
Most of these variables have a dominant manifestation and the classifier shows a low detection precision for the second manifestation.
%%
These variables include nutrition parameter, thyroid disorder and social problems induced by back pain.

%The resulting trees consist either only one rule or a rich set of them (>15).
%Either they divide the variables using only one decision rule, or a large set of rules (> 15).

\subsubsection{Concluding Remarks}
Except for gender in the age-plot, no variable could be explained with reasonable accuracy for age or body size.

@@

\com{Allgmeine Analyse der Daten mit einbringen. Hierfuer statistisch Auswertung machen, welche Parameter am meisten verwendet wurden bei der Kategorisierung. Nur Parameter verwenden, die genauer sind als 0.5\%, der Entscheidungsbaum kleiner als 15 ist und das Feature mindestens 100 Probanden enthält}

\com{Weiterhin interessant die Beschreibung rueckenschmerzassoziitierter Parameter, bei einigen zeigt sich, dass Torsion sehr dominant vertreten ist.}

\com{Algorithmus schreiben, der eng zusammenliegende Parameter fuer alle Probanden sucht.}
